% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aip,
 jmp,%
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

\begin{document}

\title[Brain Network Study During Resting States]{Brain Network Study During Resting States\\}

\author{Mattia Podio}

\author{Konstantinos Sioumalas Christodolou}%

\author{Mattias Basso}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
AbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstract AbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstract AbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstract AbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstract AbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstractAbstract AbstractAbstractAbstractAbstractAbstract
\end{abstract}

% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
\keywords{EEG data, brain network, connectivity graph, graph indices, motif analysis, community detection}%Use showkeys class option if keyword
                              %display desired
\maketitle


% \section{\label{sec:level1}First-level heading}
% \subsection{\label{sec:level2}Second-level heading}
% \subsubsection{\label{sec:level3}Third-level heading}

The goal of this project is to conduct some analysis on two datasets of EEG data. Data \cite{dataset} are taken from a public repository published from the Physionet Project. This data set consists of over 1500 one- and two-minute EEG recordings, obtained from 109 volunteers, but in our tasks we used just two runs from a specific subject (\verb|S001|): the first run - \verb|R01| - is recorded during eyes-open (EO) resting state, while the second one - \verb|R02| - is recorded during eyes-closed (EC) resting state.

Generally we worked in \verb|python|, so in order to read EEG data, that are stored in EDF format we used the \verb|pyedflib| library \cite{pyedflib}

\section{\label{sec:level1}Connectivity Graphs}

In the last decades, a big effort has been made to apply graph theory to neuroscience. For that purpose we used some basic but important tools of graph theory to identify the brain connectivity of the previous resting states.

Graph theory provides powerful means to assess topology and organization of brain connectivity networks

A network based approach is especially useful when it's important to comprehend and highlight non obvious interactions between agents in a system, their nature depending on the case study. In computational neuroscience we measure the neuronal activity of different brain regions through sensors applied on top of the scalp. Functional connectivity can be estimated using methods based on Granger causality, such as multivariate autoregressive models (MVAR).

A multivariate autoregressive model of order $p$ can be defined as 

\begin{equation}
	X(t) = \sum_{r = 1}^{p} A(r)X(t-r) + E(t)
\end{equation}

In our case, $X(t)$ is a vector that contains measurements from 64 signals at time $t$; $A(r)$ $r\in \{1,2,..p\}$ are matrices in $\mathbb{R}^{N\times N}$ that contain the parameters (to be estimated) that describe the dependence between the entries in $X(t)$ and $X(t-r)$; $E(t)$ is a vector of random variables and denotes the uncorrelated Gaussian process with zero mean.

The formula says that values at time $t$ linearly depend from the last $p$ values taken from our 64 time series through an appropriate set of $N \cdot N \cdot p$ coefficients.\\

It is possible to select the best value of $p$ with respect to the Akaike information criterion. This selection required us to spend to much time on that, and since we considered this not crucial for our purposes, we set the order of the model to $p = 3$. Further investigations can surely be made in future studies.\cite{DengfengHuang}\\

What is written above can be rewritten also like.

\begin{equation}
	\sum_{r = 0}^{p} A(r)X(t-r) = E(t)
\end{equation}

if $A(0) = \mathbb{I}$, and $A(r)$ $r\in \{1,2,3\}$ are estimated by solving the Yule Walker equations. \\

EEG signals are both defined in time as well as in frequency. We are interested in the reconstruction of the direction of information flows in the network.

Applying the Fourier Transform to both sides, hence passing to the frequency domain we have these two results

\begin{equation}
A(f)X(f) = E(f)
\end{equation}

\begin{equation}
X(f) = A^{-1}(f)E(f) = H(f)E(f)
\end{equation}


Partial Directed Coherence - PDC - is defined as 

\begin{equation}
	\pi_{ij}(f) = \frac{|A_{ij}(f)|^2}{\sum_{m=1}^{N}|A_{mi}(f)|^2}
\end{equation}

Directed Fourier Transform - DTF - is defined as 

\begin{equation}
	\theta_{ij}(f) = \frac{|H_{ij}(f)|^2}{\sum_{m=1}^{N}|H_{mi}(f)|^2}
\end{equation}

Once we calculated these estimators, choosing a particular frequency $f^*$ we can effectively start using a graph formalism: in fact what we did is to construct a graph from using either $\pi(f^*)$ or $\theta(f^*)$.

We conduct the analysis below selecting the topology that arises choosing $f^* = \text{10 Hz}$; they basically corresponds to the alpha waves (8 – 12.5 Hz), that predominantly originate from the occipital lobe during wakeful relaxation with closed eyes. Alpha waves are reduced with open eyes, drowsiness and sleep\cite{alphaPalva}.

We also generate the graphs relative to $f^* = \text{28 Hz}$, i.e. to high beta waves (20.5–28 Hz); beta states are the states associated with normal waking consciousness \cite{betaWiki}.

\section{\label{sec:level1}Graph Theory Indices}

\section{\label{sec:level1}Motif Analysis}

\section{\label{sec:level1}Community Detection}

 	
\section{References}
\begin{thebibliography}{}
	\bibitem{dataset} 
	Goldberger AL, Amaral LAN, Glass L, Hausdorff JM, Ivanov PCh, Mark RG, Mietus JE, Moody GB, Peng C-K, Stanley HE. PhysioBank, PhysioToolkit, and PhysioNet: Components of a New Research Resource for Complex Physiologic Signals. Circulation 101(23):e215-e220 [Circulation Electronic Pages; \url{http://circ.ahajournals.org/cgi/content/full/101/23/e215}]; 2000 (June 13). Dataset at \\
	\url{https://physionet.org/physiobank/database/eegmmidb/}\\
	
	\bibitem{pyedflib} \verb|pyedflib| module to read EDF files in \verb|python|. \url{https://github.com/holgern/pyedflib}\\
	
	\bibitem{DengfengHuang}
	\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4873517/}\\
	
	\bibitem{brainConEst}
	\url{https://en.wikipedia.org/wiki/Brain_connectivity_estimators}\\
	
	\bibitem{aphaFoster}
	Foster, J. J., Sutterer, D. W., Serences, J. T., Vogel, E. K., Awh, E. (2017). Alpha-Band Oscillations Enable Spatially and Temporally Resolved Tracking of Covert Spatial Attention. Psychological Science, 28(7), 929–941. \url{https://doi.org/10.1177/0956797617699167}\\
	
	\bibitem{alphaPalva}
	New vistas for $\alpha$-frequency band oscillations, Satu Palva,J. Matias Palva, Trends in Neurosciences, Elsevier, April 2007
	
	\bibitem{betaWiki}
	\url{https://en.wikipedia.org/wiki/Beta_wave}
	
\end{thebibliography}


\appendix

\section{\label{sec:level1}Figures}

\section{\label{sec:level1}Tables}



\begin{center}
	\begin{tabular}{|c|c|} 
		\hline
		Task & Class\\ [0.5ex] 
		\hline\hline
		1.1 & mandatory\\ 
		\hline
		1.2 & A\\
		\hline
		1.3 & A\\ 
		\hline
		1.5 & C\\
		\hline
		1.6 & B\\ 
		\hline
		2.1 & mandatory\\
		\hline
		2.2 & D\\ 
		\hline
		2.4 & C\\
		\hline
		2.5 & B\\ 
		\hline
		2.7 & C\\
		\hline
		3.1 & mandatory\\ 
		\hline
		3.2 & C\\
		\hline
		3.3 & C\\
		\hline
		4.1 & mandatory\\ 
		\hline
		4.2 & B\\
		\hline
		4.3 & C \\
		\hline
	\end{tabular}
\end{center}














\clearpage

\section{\label{sec:level1}First-level heading}

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended. 

\subsection{\label{sec:level2}Second-level heading: Formatting}

This file may be formatted in both the \texttt{preprint} (the default) and
\texttt{reprint} styles; the latter format may be used to 
mimic final journal output. Either format may be used for submission
purposes; however, for peer review and production, AIP will format the
article using the \texttt{preprint} class option. Hence, it is
essential that authors check that their manuscripts format acceptably
under \texttt{preprint}. Manuscripts submitted to AIP that do not
format correctly under the \texttt{preprint} option may be delayed in
both the editorial and production processes.

The \texttt{widetext} environment will make the text the width of the
full page, as on page~\pageref{eq:wideeq}. (Note the use the
\verb+\pageref{#1}+ to get the page number right automatically.) The
width-changing commands only take effect in \texttt{twocolumn}
formatting. It has no effect if \texttt{preprint} formatting is chosen
instead.

\subsubsection{\label{sec:level3}Third-level heading: Citations and Footnotes}

Citations in text refer to entries in the Bibliography;
they use the commands \verb+\cite{#1}+ or \verb+\onlinecite{#1}+. 
Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
its entire repertoire of commands are available in your document;
see the \verb+natbib+ documentation for further details.
The argument of \verb+\cite+ is a comma-separated list of \emph{keys};
a key may consist of letters and numerals. 

By default, citations are numerical; \cite{feyn54} author-year citations are an option. 
To give a textual citation, use \verb+\onlinecite{#1}+: (Refs.~\onlinecite{witten2001,epr,Bire82}). 
REV\TeX\ ``collapses'' lists of consecutive numerical citations when appropriate. 
REV\TeX\ provides the ability to properly punctuate textual citations in author-year style;
this facility works correctly with numerical citations only with \texttt{natbib}'s compress option turned off. 
To illustrate, we cite several together \cite{feyn54,witten2001,epr,Berman1983}, 
and once again (Refs.~\onlinecite{epr,feyn54,Bire82,Berman1983}). 
Note that, when numerical citations are used, the references were sorted into the same order they appear in the bibliography. 

A reference within the bibliography is specified with a \verb+\bibitem{#1}+ command,
where the argument is the citation key mentioned above. 
\verb+\bibitem{#1}+ commands may be crafted by hand or, preferably,
generated by using Bib\TeX. 
The AIP styles for REV\TeX~4 include Bib\TeX\ style files
\verb+aipnum.bst+ and \verb+aipauth.bst+, appropriate for
numbered and author-year bibliographies,
respectively. 
REV\TeX~4 will automatically choose the style appropriate for 
the document's selected class options: the default is numerical, and
you obtain the author-year style by specifying a class option of \verb+author-year+.

This sample file demonstrates a simple use of Bib\TeX\ 
via a \verb+\bibliography+ command referencing the \verb+aipsamp.bib+ file.
Running Bib\TeX\ (in this case \texttt{bibtex
aipsamp}) after the first pass of \LaTeX\ produces the file
\verb+aipsamp.bbl+ which contains the automatically formatted
\verb+\bibitem+ commands (including extra markup information via
\verb+\bibinfo+ commands). If not using Bib\TeX, the
\verb+thebibiliography+ environment should be used instead.

\paragraph{Fourth-level heading is run in.}%
Footnotes are produced using the \verb+\footnote{#1}+ command. 
Numerical style citations put footnotes into the 
bibliography\footnote{Automatically placing footnotes into the bibliography requires using BibTeX to compile the bibliography.}.
Author-year and numerical author-year citation styles (each for its own reason) cannot use this method. 
Note: due to the method used to place footnotes in the bibliography, \emph{you
must re-run BibTeX every time you change any of your document's
footnotes}. 

\section{Math and Equations}
Inline math may be typeset using the \verb+$+ delimiters. Bold math
symbols may be achieved using the \verb+bm+ package and the
\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
Blackboard (or open face or double struck) characters should be
typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
respectively. Both are supplied by the \texttt{amssymb} package. For
example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$

In \LaTeX\ there are many different ways to display equations, and a
few preferred ways are noted below. Displayed math will center by
default. Use the class option \verb+fleqn+ to flush equations left.

Below we have numbered single-line equations, the most common kind: 
\begin{eqnarray}
\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
\left(
\begin{array}{c}
|{\bf p}|+p_z\\
px+ip_y
\end{array}\right)\;,
\\
\left\{%
 \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}%
\label{eq:one}.
\end{eqnarray}
Note the open one in Eq.~(\ref{eq:one}).

Not all numbered equations will fit within a narrow column this
way. The equation number will move down automatically if it cannot fit
on the same line with a one-line equation:
\begin{equation}
\left\{
 ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}.
\end{equation}

When the \verb+\label{#1}+ command is used [cf. input for
Eq.~(\ref{eq:one})], the equation can be referred to in text without
knowing the equation number that \TeX\ will assign to it. Just
use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
the \verb+\label{#1}+ command.

Unnumbered single-line equations can be typeset
using the \verb+\[+, \verb+\]+ format:
\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \]

\subsection{Multiline equations}

Multiline equations are obtained by using the \verb+eqnarray+
environment.  Use the \verb+\nonumber+ command at the end of each line
to avoid assigning a number:
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
\delta_{\sigma_1,-\sigma_2}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_jl_i\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1),
\end{eqnarray}
\begin{eqnarray}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\nonumber \\
 & &\times \left( \sum_{i<j}\right)
  \sum_{\text{perm}}
 \frac{1}{S_{12}}
 \frac{1}{S_{12}}
 \sum_\tau c^f_\tau~.
\end{eqnarray}
\textbf{Note:} Do not use \verb+\label{#1}+ on a line of a multiline
equation if \verb+\nonumber+ is also used on that line. Incorrect
cross-referencing will result. Notice the use \verb+\text{#1}+ for
using a Roman font within a math environment.

To set a multiline equation without \emph{any} equation
numbers, use the \verb+\begin{eqnarray*}+,
\verb+\end{eqnarray*}+ format:
\begin{eqnarray*}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\\
 & &\times \left( \sum_{i<j}\right)
 \left(
  \sum_{\text{perm}}\frac{1}{S_{12}S_{23}S_{n1}}
 \right)
 \frac{1}{S_{12}}~.
\end{eqnarray*}
To obtain numbers not normally produced by the automatic numbering,
use the \verb+\tag{#1}+ command, where \verb+#1+ is the desired
equation number. For example, to get an equation number of
(\ref{eq:mynum}),
\begin{equation}
g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \tag{2.6$'$}\label{eq:mynum}
\end{equation}

A few notes on \verb=\tag{#1}=. \verb+\tag{#1}+ requires
\texttt{amsmath}. The \verb+\tag{#1}+ must come before the
\verb+\label{#1}+, if any. The numbering set with \verb+\tag{#1}+ is
\textit{transparent} to the automatic numbering in REV\TeX{};
therefore, the number must be known ahead of time, and it must be
manually adjusted if other equations are added. \verb+\tag{#1}+ works
with both single-line and multiline equations. \verb+\tag{#1}+ should
only be used in exceptional case - do not use it to number all
equations in a paper.

Enclosing single-line and multiline equations in
\verb+\begin{subequations}+ and \verb+\end{subequations}+ will produce
a set of equations that are ``numbered'' with letters, as shown in
Eqs.~(\ref{subeq:1}) and (\ref{subeq:2}) below:
\begin{subequations}
\label{eq:whole}
\begin{equation}
\left\{
 abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}
\right\},\label{subeq:1}
\end{equation}
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1).\label{subeq:2}
\end{eqnarray}
\end{subequations}
Putting a \verb+\label{#1}+ command right after the
\verb+\begin{subequations}+, allows one to
reference all the equations in a subequations environment. For
example, the equations in the preceding subequations environment were
Eqs.~(\ref{eq:whole}).

\subsubsection{Wide equations}
The equation that follows is set in a wide format, i.e., it spans
across the full page. The wide format is reserved for long equations
that cannot be easily broken into four lines or less:
\begin{widetext}
\begin{equation}
{\cal R}^{(\text{d})}=
 g_{\sigma_2}^e
 \left(
   \frac{[\Gamma^Z(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^Z(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)
 + x_WQ_e
 \left(
   \frac{[\Gamma^\gamma(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^\gamma(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)\;. \label{eq:wideeq}
\end{equation}
\end{widetext}
This is typed to show the output is in wide format.
(Since there is no input line between \verb+\equation+ and
this paragraph, there is no paragraph indent for this paragraph.)

\end{document}
%
% ****** End of file aipsamp.tex ******
